\plaintitle

### 2017-01-11 drafts/labor/conclusion.tex
release candidate 3

\begin{document}
\section{Conclusion}
\topic{On--demand work is not new, but a contemporary instantiations of piecework.}
In this paper, we reconsider three major research questions in on--demand work using the lens of piecework:
\begin{inlinelist}
  \item \nameref{sec:complexity}?
  \item \nameref{sec:decomposition}?
  \item \nameref{sec:relationships}?
\end{inlinelist}
To do so, we draw on piecework scholarship to inform analyses of what has changed, what hasn't, and may change change soon.
Reciprocally, we believe that modern on--demand work will teach us about the broader phenomenon of piecework as well.
If history really does repeat itself, the best we can do is be prepared.

>>>>

\begin{document}
\section{Conclusion}
\topic{On--demand work is not new, but a contemporary instantiation of piecework.}
In this paper, we reconsider three major research questions in on--demand work using piecework as a lens:
\begin{inlinelist}
  \item \nameref{sec:complexity}?
  \item \nameref{sec:decomposition}?
  \item \nameref{sec:relationships}?
\end{inlinelist}
We draw on piecework scholarship to inform analyses of what has changed, what hasn't, and may change soon.
Reciprocally, we believe that modern on--demand work can teach us about the broader phenomenon of piecework as well.
If history really does repeat itself, the best we can do is be prepared.

\section{Acknowledgements}
This work was supported by the Stanford Cyber Initiative and National Science Foundation award IIS-1351131.

### 2017-01-11 drafts/labor/discussion.tex
release candidate 3

But this does not mean that attempting to draw meaningfully from historical scholarship would be folly;
enough of piecework can and does inform on--demand work that
HCI and CSCW might seek out historical framings for other phenomena of study as well.
While we can only speculate one of (perhaps many) possible futures, history does allow us to articulate and bound which futures appear more likely.

@@

\subsection{Utopian and Dystopian Visions}\label{sec:polarizationOfCrowdWork}
\topic{An easy narrative is to characterize the future of on--demand labor at one of two extremes.}
On one hand, crowd work researchers
imagine the application of crowdsourcing as
a potentially bright future that enables the achievement of near--impossible goals and career opportunities~\cite{redballoon,crowdworkFuture,vizwiz,suzukiAtelier}.
On the other hand, researchers
warn that on--demand labor will create exploitative sites of dispossession~\cite{scholz2012digital},
racial discrimination~\cite{edelman2015racial},
and invisible, deeply frustrated workers~\cite{turkopticon,bighamHalfWorkday}.

@@

\topic{On the other hand, while piecework's nascent years were grim, 
they precipitated a century of some of the most potent labor advocacy organizations in modern history~\cite{hart2013rise,mccallum2013global}.}
Even today, the \textit{geist} of the labor union revolution
inspires collective action and worker empowerment around the world.
Recently, in India, workers across the nation engaged in
the largest labor strike in human history
\cite{indiaStrikeRealNews}.
If labor advocacy groups can find ways to effect change in on--demand work as some have called for
\cite{futureUnions},
then the future of on--demand labor may follow
the same trajectory of worker empowerment that piecework saw.

\topic{The history of piecework suggests that the utopian and dystopian outcomes will \textit{both} occur, in different parts of the world and to different people.}
When piecework plummeted in the United States, outsourcing rose --- creating major labor issues around the world.
It is entirely possible that we will create a new brand of flexible online career in developed countries, while simultaneously fueling an unskilled decentralized labor force in developing nations.
As designers and researchers, this prompts the question: which outcome are we attempting to promote or avoid for who?

@@

While we have arguably outpaced piecework with regard to the limits on the complexity of work,
the most complex and open-ended wicked problems~\cite{rittel1973dilemmas} remain the domain of older human collectives such as governments and organizations. 
In addition, we can learn from the piecework literature as it relates to
the stymieing effect that mismanagement has on workers;
research into the complexity limits should emphasize on finding new ways to manage workers,
in particular using humans --- perhaps other crowd workers ---
to act as modern foremen.

Piecework researchers looking into decomposition pointed out long ago that
piecework is saddled by a lower limit on decomposition:
``piecework does not compensate workers for time spent switching tasks''~\cite{bewley1999wages}. % Chinmay wanted me to specifically call out that this is from chapter 6. Is that necessary...?
\ali{Chinmay: <suggestion to look at \cite{stigler1962information} and friction> --- not sure if worth getting into.}
We've since studied this phenomenon in crowd work to great length both
observationally \cite{taskSearch} and
experimentally \cite{delayAndOrderLasecki}.
We should consider whether this remains a worthwhile area to explore;
unless the work we put forth directly affects the costs of task--switching
--- for instance, the cost of suboptimal task search, or the cognitive burden of changing tasks ---
we may only make incremental advances in micro--task decomposition.
When the cognitive cost of understanding a task and its inputs outstrips the effort required to complete the task, decomposition seems a poor choice.

Finally, we turn to the relationships of crowd workers.
The crowd work literature here can convincingly speak back to
the piecework scholarship perhaps more than in the other sections.
The tools that are available to us today
--- not just technical, but \textit{methodological} ---
make it possible to
discover,
study, and
partner with 
crowd workers in ways that were unimaginable to piecework researchers.
A professor engages in crowd work~\cite{bighamHalfWorkday}
not just because it's possible, but because our community
appreciates the importance of approaches such as participant--observation and ethnography as a whole~\cite{olson2014ways}.

\ali{
Discussions from Slack:

Chinmay: I think the most provocative claim is ``The history of piecework suggests that the utopian and dystopian outcomes will both occur, in different parts of the world and to different people.''\\
seems contrary to the idea that marketplaces are global\\
I would also like some more thought into the Research Agenda section\\

Ali: so the dystopian and utopian claim is partly influenced by the fact that piecework seemed to affect some industries differently than others\\

Chinmay: ah ok\\
i think you could claim the same about online piecework\\
differnt industries\\

Ali: garment-makers were pretty thoroughly marginalized, but industrial metalwork led to this whole WWII phenomenon with expert training\\
mmmm\\
but now it's not just about the industry, but about the design of the labor market\\
we can influence the ``architecture'' in a way that we couldn't before\\
this is all lessig and stuff\\

Chinmay: oh\\
i understand\\
hmm something there\\
might poke more :)

\dotfill

Chinmay> i wish you had a little more criticality in taylorism but I'm a downer :)

Ali> actually a reviewer wanted more on taylorism but i was afraid that we just didn't have the space to really give anyone into taylorism what they want

Chinmay> essentially that would be a great place to talk about how those three questions you mentioned interact

Ali> oh
that might be worth fitting in
i mean we inexplicably got it down to 9.5 pages or so
or 9.75
we were over for like 99% of the drafting and then inexplicably something just imploded and we got like half a page
so yeah i'll try and write something giving taylorism more space and using that to talk about the confluence of these three questions
}

>>>>

But this does not mean that attempting to draw meaningfully from historical scholarship would be folly;
enough of piecework can and does inform on--demand work that
HCI and CSCW researchers might seek out historical framings for other phenomena of study as well.
While we can only speculate one of (perhaps many) possible futures, history does allow us to articulate and bound which futures appear more likely.

@@

\subsection{Utopian and Dystopian Visions}\label{sec:polarizationOfCrowdWork}
\topic{An easy narrative is to characterize the future of on--demand labor at one of two extremes.}
On one hand, crowd work researchers
imagine the application of crowdsourcing as
a potentially bright future that enables the achievement of near--impossible goals and career opportunities~\cite{redballoon,crowdworkFuture,vizwiz,suzukiAtelier}.
On the other hand, researchers
warn that on--demand labor will create exploitative sites of dispossession~\cite{scholz2012digital},
discrimination~\cite{edelman2015racial},
and invisible, deeply frustrated workers~\cite{turkopticon,bighamHalfWorkday}.

@@

\topic{On the other hand, while piecework's nascent years were grim, 
what followed was a century of some of the most potent labor advocacy organizations in modern history~\cite{hart2013rise,mccallum2013global}.}
Even today, the \textit{geist} of the labor union revolution
inspires collective action and worker empowerment around the world.
Recently, in India, workers across the nation engaged in
the largest labor strike in human history~\cite{indiaStrikeRealNews}.
If labor advocacy groups can find ways to effect change in on--demand work as some have called for~\cite{futureUnions},
then the future of on--demand labor may follow
the same trajectory of worker empowerment that piecework saw.

\topic{The history of piecework suggests that the utopian and dystopian outcomes will \textit{both} occur,
in different parts of the world and to different groups of people.}
When piecework largely disappeared in the United States, outsourcing appeared --- creating major labor issues around the world.
It'ss entirely possible that we will create a new brand of flexible online career in developed countries,
while simultaneously fueling an unskilled decentralized labor force in developing nations.
As designers and researchers, this prompts the question: which outcome are we attempting to promote or avoid for whom?

@@

While we have arguably outpaced piecework with regard to the limits on the complexity of work,
the most complex and open--ended wicked problems~\cite{rittel1973dilemmas} remain the domain of older human collectives such as governments and organizations. 
In addition, we can learn from the piecework literature as it relates to
the stymieing effect that mismanagement has on workers;
research into complexity limits should focus on finding new ways to manage workers,
in particular using humans (perhaps other crowd workers)
to act as modern ``foremen''.

Piecework researchers looking into decomposition pointed out long ago that
piecework is saddled by a lower limit on decomposition:
as \citeauthor{bewley1999wages} mentions,
``piecework does not compensate workers for time spent switching tasks''~\cite{bewley1999wages}. 
We've since studied this phenomenon in crowd work both
observationally \cite{taskSearch} and
experimentally \cite{delayAndOrderLasecki}.
We should consider whether this remains a worthwhile area to explore;
unless the work we put forth directly affects the costs of task--switching
--- for instance, the cost of suboptimal task search, or the cognitive burden of changing tasks ---
we may only make incremental advances in micro--task decomposition.
When the cognitive cost of understanding a task and its inputs outstrips the effort required to complete it, decomposition seems a poor choice.

Finally, we turn to the relationships of crowd workers.
The crowd work literature here can convincingly speak back to
the piecework scholarship perhaps more than in the other sections.
The tools that are available to us today
--- not just technical, but \textit{methodological} ---
make it possible to
discover, study, and partner with 
crowd workers in ways that were unimaginable to piecework researchers.
\citeauthor{bighamHalfWorkday} engages in crowd work~\cite{bighamHalfWorkday}
not just because it's possible, but because our community
appreciates the importance of approaches such as participant--observation and ethnography as a whole~\cite{olson2014ways}.

We should also take a moment to explore the opportunity to discuss the ethics of on--demand labor,
as \citeauthor{williamson2016} does~\cite{williamson2016}.
The literature on the history of piecework does not
frame the question as \textit{whether piecework is inherently ethical or unethical},
instead asking \textit{what conditions render it exploitative}.
The literature we have brought to bear suggests that exploitation occurs when
conditions harm workers directly or indirectly, such as
in sweatshops and agricultural work with pesticides, or where
employers systematically underpay or overwork laborers by contemporary standards.

The question then is
whether given socio--technical infrastructures 
systematically harm, underpay, or overwork workers.
For example, Amazon Mechanical Turk does not directly require any rate of payment for work,
but its design encourages employers to engage in exploitative behavior:
piece--rate pay, for example, does not value workers' task search time;
additionally, task design interfaces undeniably frame
workers as unreliable by recommending
replication with multiple workers rather than
trusting and paying individual workers more.

Piecework also has lessons for a number of other research questions in crowdsourcing.
For example, future work could more deeply explore the evolution of
scientific management as it relates to
crowdsourcing optimization;
quality control approaches between the two eras; and
further analysis of incentive structures.

### 2017-01-11 drafts/labor/relationships.tex
release candidate 3

HCI and CSCW have historically framed themselves around supporting work.
While all artifacts have politics,
the recent shift into computational labor systems has directly impacted
the lives and livelihood of workers in new ways.
So, it is important to understand:
what will the future look like for the workers who use these systems?

\subsubsection{\crowdworkpers}
\begin{comment}
	- Workers do it for money
	- Workers coordinate and communicate (gray, being a turker, team stuff). there is mega-drama
	- Workers don't like requesters. have tried to organize
\end{comment}

Who are the crowd workers and what draws them to crowd work?
Early literature emphasized motivations like fun and spare change, but this narrative soon shifted to emphasize that many workers use platforms such as Amazon Mechanical Turk as a primary source of income~\cite{kaufmann2011more,ipeirotis2010demographics,Antin2012a}.
Despite this, Mechanical Turk is a low-wage affair for most workers in the United States~\cite{ipeirotis2010demographics,martin2014being,gupta2014turk}.
Thus, those who choose to opt out of the traditional labor force and spend significant time on Mechanical Turk are especially motivated by the opportunity for autonomy and skill variety~\cite{kaufmann2011more}.
While some carry attitudes of ``pity the workers'' toward Turkers, this frame is increasingly rejected by workers and designers as patronizing~\cite{storiesIraniSilberman}.

Workers' relationships with requesters are fraught.
The unbridled power that requesters have over workers, and
the resultant frustration that this generates,
has motivated research into
the tense relationships between workers and requesters~\cite{fixingChaos,dynamo}.
Workers are often blamed for any low-quality work, regardless of whether they are responsible~\cite{martin2014being,takingAHITMcInnis}.
Some research is extremely open about this position, blaming unpredictable work on ``malicious'' workers~\cite{MaliciousCrowdworkersGadiraju} or those with ``a lack of expertise, dedication [or] interest''~\cite{Sheng:2008:GLI:1401890.1401965}.
Workers resent this position --- for good reason.
\citeauthor{turkopticon} highlighted the information asymmetry between workers and requesters on AMT, leading to the creation of \TO, a site which allows Turkers to rate and review requesters~\cite{turkopticon}.
Dynamo then took this critique on information asymmetry and power imbalances a step further, designing a platform to facilitate
Turkers acting collectively to bring about changes to their circumstances~\cite{dynamo}.

Researchers have also begun to appreciate the sociality of crowd workers.
Because the platforms do not typically include social spaces, workers instead congregate off-platform in forums and mailing lists.
There, Turkers exchange advice on high-paying work, talk about their earnings, build social connections, and discuss requesters~\cite{martin2014being}.
Many crowd workers know each other through offline and online connections, coordinating behind-the-scenes despite the platforms encouraging independent work~\cite{crowdcollab,yin2016communication}.
However, the frustration and mistrust that workers experience with requesters does occasionally boil over on the forums. 
%This behavior has come to be known as ``mega--drama'' amongst such workers~\cite{dynamo}.
%Still, the study of these communities is made challenging because most of these platforms do not themselves include social affordances for workers~\cite{miller2011understanding}.

@@

\topic{Early observers believed that workers were strongly motivated by the autonomy of working in the piecework model}.
\citeauthor{clark1908cotton} observed textile mill pieceworkers and reported,
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand.''
However, the emergent trend contrasted with this early rhetoric, as
when workers began instituting ``The Fix'', deliberately slow work to game efficiency experts~\cite{roy1954efficiency}.
Piece workers, \citeauthor{roy1954efficiency} found, would form even more starkly antagonistic relationships with their managers.

\topic{Soon workers began resisting piecework regimes.}
The match--girls engaged in their famous strike of 1888, particularly pushing to abolish the fines that were taken out of their wages.
Soon others followed suit, including women in the garment industry in Philadelphia who established collective bargaining rights~\cite{10.2307/41829256} and national coal miners who effected an individual minimum wage in 1912~\cite{10.2307/2221944}.

Many worker organizations began weighing in on
(or, more precisely, against)
piecework and the myriad oversights it made in valuing workers' time~\cite{american1921problem,richards1904anything}.
As mounting attention increasingly revealed problems in piecework's treatment of workers,
workers themselves began to speak out about their frustration with this new regime.
Organizations representing
railway workers,
mechanical engineers, and
others began to mount advocacy in defense of workers~\cite{american1921problem,richards1904anything}.
Pieceworkers' relationships with their employers eventually developed a pattern of using 
laborer advocacy groups~\cite{levi2009union,ahlquist2013interest,mccallum2013global,jacoby1983union}.
Following the template of the match--girls, collective action grew to become a central component of negotiating with managers~\cite{russell1982collective,olsonlogic}.

\topic{Relative to the modern on--demand workers, there is a noticeable dearth of information on the inter--personal relationships among pieceworkers
beyond the match--girls at the end of the \nth{19} century.}
Nevertheless, we can offer some observations:
primary sources indicate that labor organizations wished for workers to identify as a collective group, 
``not only as railroad employees but also as members of the larger life of the community''~\cite{american1921problem}.
Doing this, 
\citeauthor{ostrom1990governing} and others later argued,
would facilitate collective action and perhaps collective governance~\cite{ostrom1990governing,russell1982collective,olsonlogic}.
\citeauthor{riisOtherSideLives} also contributed to this sense of shared struggle and endurance
by documenting pieceworkers in their home--workplaces,
literally bringing to light the grim circumstances in which pieceworkers lived and worked~\cite{riisOtherSideLives}.

@@

There was generally less written about work quality concerns for historical pieceworkers than there is in modern on--demand work. 
Why the difference? 
One possibility is that, through writing web scripts and applying them to many tasks, it is possible for a small number of spammers have an outsized influence.
Another possibility is that historical pieceworkers faced much more risk in shirking: it was much harder for piece workers to move to a new location and find a new job. Today, Mechanical Turk workers can simply accept a different task.
A third possibility: online anonymity breeds distrust~\cite{friedman2000trust}, and where pieceworkers could be directly observed by foremen and known to them, online workers are known by little more than an account ID.

\topic{The relationship between workers and employers has also shifted: while historically the management of workers had to be done through a foreman
(who necessarily had an intuitive
--- perhaps sympathetic ---
relationship with workers),
the foremen of the \nth{20} century has largely been replaced
by the algorithms of the \nth{21} century~\cite{uberAlgorithm}.}
The result of this change is that the agents managing work are now
cold, logical, and unforgiving.
Where a person might recognize that the ``attention check'' questions
proposed by \citeauthor{le2010ensuring} and others ensure that
malicious and inattentive workers are stopped~\cite{le2010ensuring,AAAIW113995},
some implementations of these approaches
only seem to antagonize workers~\cite{takingAHITMcInnis}.
More than 30 years ago, \citeauthor{10.2307/2555446} wrote:
``When performance is difficult to evaluate,
imperfect input measures and
a manager's subjective judgment are preferable to
defective (simple, observable) output measures''~\cite{10.2307/2555446}.
This frustration has only grown as requesters have had to rely on automatic management mechanisms. Only a few use the equivalent of human foremen~\cite{haas2015argonaut,kulkarni2012mobileworks}.

Relative to the mature state of collective action for pieceworkers offline,
crowd workers have struggled to make their voices heard~\cite{dynamo,storiesIraniSilberman,turkopticon}.
%Both pieceworkers and on--demand workers have struggled at times to form a collective identity necessary to organize.
With workers joining and leaving the on--demand labor force continuously, and with many part-time members, it is extremely difficult to corral the group to make a collective decision~\cite{dynamo}.
However, even when they can, enforcement remains a challenge: whereas pieceworkers could physically block access to a site of production, online labor markets provide no facilities for workers to change the experience of other workers.
This is a key limitation --- without it, workers cannot enforce a strike.

@@

\topic{Reciprocally, crowd work may be able to inform piecework research in this domain.}
There exists far less literature about piece workers' relationships than there does today about on--demand workers' relationships.
Two reasons stand out: first, modern platforms are visible to researchers in ways that the sites of piece work labor were not.
Second, Anthropology stands on a firmer theoretical and methodological basis than it did at the turn of the \nth{20} century.
Malinowski, Boas, Mead, and
% \citeauthor{malinowski2002argonauts,boas1940race,mead1973coming} and % this was naming Boas twice, so.
other luminaries throughout the first half of the \nth{20} century
effectively defined Cultural Anthropology as we know it today;
\textit{participant--observation},
the \textit{etic} and the \textit{emic} understanding of culture, and
\textit{reflexivity}
didn't take even a resemblance of their contemporary forms until these works~\cite{malinowski2002argonauts,boas1940race,mead1973coming}.
On--demand labor today may give us an opportunity to revisit open questions in piecework with a more refined lens.

>>>>

HCI and CSCW have historically framed themselves around supporting work.
While all artifacts have politics,
the recent shift into computational labor systems has directly impacted
the lives and livelihoods of workers in new ways.
So, it's imperative to ask:
What will the future look like for the workers who use these systems?

\subsubsection{\crowdworkpers}
\begin{comment}
	- Workers do it for money
	- Workers coordinate and communicate (gray, being a turker, team stuff). there is mega--drama
	- Workers don't like requesters. have tried to organize
\end{comment}

Who are the crowd workers and what draws them to crowd work?
Early literature emphasized motivations like fun and spare change, but this narrative soon shifted to emphasize that many workers use platforms such as Amazon Mechanical Turk as a primary source of income~\cite{kaufmann2011more,ipeirotis2010demographics,Antin2012a}.
Despite this, Mechanical Turk is a disappointingly low--wage worksite for most people in the United States~\cite{ipeirotis2010demographics,martin2014being,gupta2014turk}.
Thus, those who choose to opt out of the traditional labor force and spend significant time on Mechanical Turk are especially motivated by the opportunity for autonomy and transience between tasks~\cite{kaufmann2011more}.
While some describe Turkers as powerless victims or even unaware of what's going on,
this framing is increasingly being rejected by workers and designers as
``cast[ing] Turkers as dopes in the system.''~\cite{storiesIraniSilberman}.

Workers' relationships with requesters are fraught.
The unbridled power that requesters have over workers, and
the resultant frustration that this generates,
has motivated research into
the tense relationships between workers and requesters~\cite{fixingChaos,dynamo}.
Workers are often blamed for any low--quality work, regardless of whether they are responsible~\cite{martin2014being,takingAHITMcInnis}.
Some research is extremely open about this position, blaming unpredictable work on ``malicious'' workers~\cite{MaliciousCrowdworkersGadiraju} or those with ``a lack of expertise, dedication [or] interest''~\cite{Sheng:2008:GLI:1401890.1401965}.
Workers resent this position, and for good reason.
\citeauthor{turkopticon} highlighted the information asymmetry between workers and requesters on AMT,
which led to the creation of Turkopticon, a site which allows Turkers to rate and review requesters~\cite{turkopticon}.
Dynamo then took this critique on information asymmetry and power imbalances further, designing a platform to facilitate
collective action among Turkers to changes to their circumstances~\cite{dynamo}.

Researchers have also begun to appreciate the sociality of crowd workers.
Because the platforms do not typically include social spaces, workers instead congregate off--platform in forums and mailing lists.
There, Turkers exchange advice on high--paying work, talk about their earnings, build social connections, and discuss requesters~\cite{martin2014being}.
Many crowd workers know each other through offline and online connections, coordinating behind--the--scenes despite the platforms encouraging independent work~\cite{crowdcollab,yin2016communication}.
However, the frustration and mistrust that workers experience with requesters does occasionally boil over on the forums. 
%This behavior has come to be known as ``mega--drama'' amongst such workers~\cite{dynamo}.
%Still, the study of these communities is made challenging because most of these platforms do not themselves include social affordances for workers~\cite{miller2011understanding}.

@@

\topic{Early observers believed that workers were strongly motivated by the autonomy of working in the piecework model}.
\citeauthor{clark1908cotton} observed textile mill pieceworkers and reported,
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand''~\cite{clark1908cotton}.
However, the emergent trend contrasted with this early rhetoric, as
when workers began instituting ``The Fix'', deliberately slow work to game efficiency experts~\cite{roy1954efficiency}.
Piece workers, \citeauthor{roy1954efficiency} found, would form acrimonious relationships with their managers.

\topic{Soon, workers began resisting piecework regimes.}
The match--girls engaged in their famous strike of 1888, particularly pushing to abolish the fines that were taken out of their wages.
Soon others followed suit, including women in the garment industry in Philadelphia who established collective bargaining rights~\cite{10.2307/41829256} and national coal miners who effected an individual minimum wage in 1912~\cite{10.2307/2221944}.

Many worker organizations began weighing in against
% (or, more precisely, against)
piecework and the myriad oversights it made in valuing workers' time~\cite{american1921problem,richards1904anything}.
As mounting attention increasingly revealed problems in piecework's treatment of workers,
workers themselves began to speak out about their frustration with this new regime.
Organizations representing
railway workers,
mechanical engineers, and
others began to mount advocacy in defense of workers~\cite{american1921problem,richards1904anything}.
Pieceworkers' relationships with their employers eventually developed a pattern of using 
laborer advocacy groups~\cite{levi2009union,ahlquist2013interest,mccallum2013global,jacoby1983union}.
Following the template of the match--girls, collective action grew to become a central component of negotiating with managers~\cite{russell1982collective,olsonlogic}.

\topic{Relative to the modern on--demand workers, there is a noticeable dearth of information on the interpersonal relationships among pieceworkers
beyond the match--girls at the end of the \nth{19} century.}
Nevertheless, we can offer some observations:
primary sources indicate that labor organizations wished for workers to identify as a collective group, 
``not only as railroad employees but also as members of the larger life of the community''~\cite{american1921problem}.
Doing this, 
\citeauthor{ostrom1990governing} and others later argued,
would facilitate collective action and perhaps collective governance~\cite{ostrom1990governing,russell1982collective,olsonlogic}.
\citeauthor{riisOtherSideLives} also contributed to this sense of shared struggle and endurance
by documenting pieceworkers in their home--workplaces,
literally bringing to light the grim circumstances in which pieceworkers lived and worked~\cite{riisOtherSideLives}.

@@

There was generally less written about work quality concerns for historical pieceworkers than there is in modern on--demand work. 
Why the difference? 
One possibility is that, by writing web scripts and applying them to many tasks,
a small number of spammers have an outsized influence on the perception of bad actors.
Another possibility is that historical pieceworkers faced much more risk in shirking:
it was much harder for pieceworkers to move to a new location and find a new job.
Today, Mechanical Turk workers can work for a dozen or more different groups in the span of a day.
A third possibility: online anonymity breeds distrust~\cite{friedman2000trust}, and
where pieceworkers could be directly observed by foremen and known to them,
online workers are known by little more than an inscrutible alphanumeric string, like A2XJMS2J2FMVXK.

\topic{The relationship between workers and employers has also shifted: while historically the management of workers had to be done through a foreman,
% (who necessarily had an intuitive
% --- perhaps sympathetic ---
% relationship with workers),
foremen of the \nth{20} century have largely been replaced
by algorithms of the \nth{21} century~\cite{uberAlgorithm}.}
% The result of this change is that
Consequently,
the agents managing work are now
cold, logical, and unforgiving.
While a person might recognize that the ``attention check'' questions
proposed by \citeauthor{le2010ensuring} and others ensure that
malicious and inattentive workers are stopped~\cite{le2010ensuring,AAAIW113995},
some implementations of these approaches
only seem to antagonize workers~\cite{takingAHITMcInnis}.
As \citeauthor{10.2307/2555446} wrote in \citeyear{10.2307/2555446},
``when performance is difficult to evaluate,
imperfect input measures and
a manager's subjective judgment are preferable to
defective (simple, observable) output measures''~\cite{10.2307/2555446}.
This frustration has only grown as requesters have had to rely on automatic management mechanisms.
Only a few use the equivalent of human foremen~\cite{haas2015argonaut,kulkarni2012mobileworks}.

Relative to the history of collective action for pieceworkers,
on--demand workers have struggled to make their voices heard~\cite{dynamo,storiesIraniSilberman,turkopticon}.
With workers constantly drifting through these platforms, and with many part--time members,
it's extremely difficult to corral the group to make a collective decision~\cite{dynamo}.
Even when they can, enforcement remains a challenge:
while pieceworkers could physically block access to a site of production and convince other workers to join them,
online labor markets provide no facilities for workers to change the experience of other workers.
This is a key limitation --- without it, workers cannot enforce a strike.

@@

\topic{Reciprocally, crowd work may be able to inform piecework research in this domain.}
There exists far less literature about piece workers' relationships than there does today about on--demand workers' relationships.
Two reasons stand out: first, modern platforms are visible to researchers in ways that the sites of piece work labor were not.
Second, Anthropology stands on a firmer theoretical and methodological basis than it did at the turn of the \nth{20} century.
Malinowski, Boas, Mead, and
other luminaries throughout the first half of the \nth{20} century
effectively defined Cultural Anthropology as we know it today;
\textit{participant--observation},
the \textit{etic} and the \textit{emic} understanding of culture, and
\textit{reflexivity}
didn't take even a resemblance of their contemporary forms until these works~\cite{malinowski2002argonauts,boas1940race,mead1973coming}.
On--demand labor today may give us an opportunity to revisit open questions in piecework with a more refined lens.
